Descriptives for potential paper 1 

### 2022-07-01 msdepression/scripts/Descriptives_potential_paper_1_20220622.Rmd
Add files via upload

---
title: "Descriptives for potential paper 1 "
author: "Erica Baller"
date: "Started 2022 06 22"
output:
  html_document: default
  pdf_document: default
---

@@

Results
  *Demographics
    total n unique subjects = 783 (F = 609, M = 174) 
    total scans = 2962 (F = 2270, M = 692)

  *Age effects (unique):
      -Age mean 47 (range 20-83). 
      -Almost everything corrects (59 out of 87 fascicles, 26 in association network)
      -Take home - as expected, the older you are, the worse white matter fascicle invovlement you have

  *Age effects (gam unique)
      - 62 out of 87 fascicles correct, 26 in association network

  *Age effects (mixed model)
      - 57 out of 87 correct, 27 in association network

  *Sex effects (unique):
      - In the final good MIMoSA group, there were 609 unique females and 174 unique males, 77% women
      - Individual fascicle results underwhelming, only 3 regions meet P<0.05 (unc), 
          SCP	0.020859515			
          CPT_F_R	0.040590173			
          CPT_O_R	0.049616343			
          CPT_P_R	0.032079145			
          DRTT_L	0.047328252			
          DRTT_R	0.008453751			
          ML_R	0.033199761			
          OR_R	0.039151847

@@

  *Sex effects (mixed model):
      - no action
      - Individual fascicle results w/ 12 that meet P<0.05 (uncorrected)
          ICP_L	0.016204905			
          MCP	0.002505451			
          SCP	0.005273532			
          V	0.018452360			
          CNVIII_L	0.005692622			
          CPT_F_R	0.047149209			
          CPT_O_R	0.031170467			
          CPT_P_R	0.025315969			
          CST_R	0.039553847			
          DRTT_L	0.043957171

  * Age*sex (unique)
      - no action

  * Age * sex (mixed model) 
  lmerTest::lmer(substitute(i ~ PAT_AGE_AT_EXAM*osex + (1|EMPI), list(i = as.name(x))), data = df_mm)
      - Action!
      - Age term: 55/87 correct
      - Sex Term: 1 (Fornix_R) corrects
      - Age*Sex intx term: 1 (fornix_R) corrects
      - Age *sex uncorrected (5):
          UF_L	0.0114639855			
          CNVIII_R	0.0163558293			
          CNVII_R	0.0175275993			
          CBT_L	0.0260870383			
          F_R	0.0002210451

@@

#fdr corrected only association cortex
fascicle_anova_w_fiber_mapping <- fascicle_age_anova[which(fascicle_bundle_mapping$name_vector == "association")]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr_association)

>>>>

---
title: "Descriptives for potential paper 1 "
author: "Erica Baller"
date: "Started 2022 06 22"
output:
  pdf_document: default
  html_document: default
---

@@

Results

  *Demographics*

    total n unique subjects = 783 (F = 609, M = 174) 
    total scans = 2962 (F = 2270, M = 692)

  *Age effects (unique): *

      -Age mean 47 (range 20-83). 
      -Almost everything corrects (59 out of 87 fascicles, 26 in association network)
      -Take home - as expected, the older you are, the worse white matter fascicle invovlement you have

  *Age effects (gam unique)*

      - 62 out of 87 fascicles correct, 26 in association network

  *Age effects (mixed model)*

      - 57 out of 87 correct, 27 in association network

  *Sex effects (unique):*

      - In the final good MIMoSA group, there were 609 unique females and 174 unique males, 77% women
      - Individual fascicle results underwhelming, P<0.05 (unc), 
          SCP	0.020859515			
          CPT_F_R	0.040590173			
          CPT_O_R	0.049616343			
          CPT_P_R	0.032079145			
          DRTT_L	0.047328252			
          DRTT_R	0.008453751			
          ML_R	0.033199761			
          OR_R	0.039151847

@@

  *Sex effects (mixed model):*

      - no action
      - Individual fascicle results w/ 12 that meet P<0.05 (uncorrected)
          ICP_L	0.016204905			
          MCP	0.002505451			
          SCP	0.005273532			
          V	0.018452360			
          CNVIII_L	0.005692622			
          CPT_F_R	0.047149209			
          CPT_O_R	0.031170467			
          CPT_P_R	0.025315969			
          CST_R	0.039553847			
          DRTT_L	0.043957171

  *Agexsex (unique)*

      - no action

  *Agexsex (mixed model) *

  lmerTest::lmer(substitute(i ~ PAT_AGE_AT_EXAM*osex + (1|EMPI), list(i = as.name(x))), data = df_mm)
      - Action!
      - Age term: 55/87 correct
      - Sex Term: 1 (Fornix_R) corrects
      - Age*Sex intx term: 1 (fornix_R) corrects
      - Age *sex uncorrected (5):
          UF_L	0.0114639855			
          CNVIII_R	0.0163558293			
          CNVII_R	0.0175275993			
          CBT_L	0.0260870383			
          F_R	0.0002210451

@@

#fdr corrected only association cortex
fascicle_bundle_mapping=get_fascicle_bundle_mapping()
fascicle_anova_w_fiber_mapping <- fascicle_age_anova[which(fascicle_bundle_mapping$name_vector == "association")]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr_association)
